---
title: "getJatosData"
author: "Noah Rischert"
format: html
editor: source
editor_options: 
  chunk_output_type: console
---

# 1 Initial setting

## 1.1 clear workspace and set default color

```{r reset, include=FALSE}
# Clear everything
graphics.off()
rm(list = ls(all.names = TRUE)) 
gc()

# Set base R options
options(digits = 3)

# (Optional) Set some color defaults if desired
options(
  ggplot2.discrete.colour = c("#615F63","#FF7F6F","#2F7FC1","#FFBE7A","#8FC0A9","#8A1C56"),
  ggplot2.discrete.fill   = c("#615F63","#FF7F6F","#2F7FC1","#FFBE7A","#8FC0A9","#8A1C56")
)
```

## 1.2 Import functions and packages

```{r}

# If not installed, install the 'smartr' package from the 'develop' branch:
# devtools::install_github("chenyu-psy/smartr@develop")

# remotes::install_github("paul-buerkner/brms")

# Load your packages
library(bmm)
library(ggplot2)
library(dplyr)
library(Rmisc)
library(tidyverse)
library(smartr)
library(circular)
library(purrr)
library(glue)    
library(brms)
library(rstan)
library(parallel)
library(bayestestR) # For Bayesian post-processing (Bayes factors, etc.)
library(smartr)
source("functions/pairwise_comparisons.R")
source("functions/lineplot.ci3.R")
source("functions/lineplot.ci4.R")


# (Optional) Set a default ggplot theme
theme_set(theme_bw())
dodge2 <- position_dodge(0.2)

```

# 2 Data Preparation

## 2.1 Import data

``` {r}
# This function downloads data from JATOS and returns metadata about the downloaded files.

# Replace "your_api_token" with your actual JATOS API token,
# and "123, 124" with the relevant batch IDs in your experiment.
# The dataPath argument is optional; defaults to a "JATOS_DATA" folder if not specified.

metadata <- get_JATOS_data(
  token       = "jap_xqlMnZelpmfnJ1GuSATq1ChUuVtHh8g951636", 
  batchId     = "911",          # one or more batch IDs
  dataPath    = "data/raw/",   # or another folder
  attachments = FALSE
)

```

## 2.2 Read metadata, filter it

``` {r}
# If you already have metadata saved from a previous run, you can read it directly:
# Adjust the file path (here, it's inside "downloaded_data").

metadata <- read_metaData("data/raw/metadata.json")

# Filter out incomplete runs
completed_data <- metadata %>% 
  filter(fileSize > 500)


```

## 2.3 Read and Combine Data

``` {r}
# Read the JSON data files associated with your completed runs
# (NA paths are automatically excluded)
combinedData <- read_json_data(completed_data$file)

# Check structure or run a simple summary
summary(combinedData)

# Save study_data as an RDS
saveRDS(combinedData, "data/raw/experiment2.rds")
# You can now do further data wrangling, visualization, or modeling with study_data
```

# 3 Prepare Data

## 3.1 Keep relevant columns that are not practice, and rows from the recall trials (isTestTrial == TRUE)

``` {r}
declutteredData <- combinedData %>%
  filter(isTestTrial == TRUE & practice == FALSE) %>%
  select(
    rt, participant, subject, blockOrder, trialType,
    recallOrderinMixed = recallOrder, # Rename "recallOrder" to "recallOrderinMixed", because that is what it really is
    blockID, segmentID, trialID, practiceTrialID, 
    numCircles, recallPosition, AorBatRetrieval, side, 
    stimulusToIdentify, selectedStimuli, click_x, click_y
  )

# Create setSize with either 3 or 6 for the trials where items were split into two groups of 3, since we do consider those trials to equate to 6 total items.
declutteredData <- declutteredData %>%
  mutate(
    setSize = if_else(
      trialType == "split" & numCircles == 3,
      6,            # When condition is TRUE, setSize becomes 6
      numCircles    # Otherwise, keep the existing number of circles
    )
  )

# Replace NA with none so brms can handle it better
declutteredData <- declutteredData %>%
  mutate(
    AorBatRetrieval = if_else(
      is.na(AorBatRetrieval), 
      "none", 
      AorBatRetrieval
    )
  )

# Create a new column which combines whether a row (= specific response) was presented grouped, separated, and if it was separated, whether it was predictable or unpredictable
declutteredData <- declutteredData %>%
  mutate(
    presentationType = case_when(
      trialType == "combined" ~ "grouped",
      trialType == "split" & recallOrderinMixed == "ABBA"   ~ "separate_predictable",
      trialType == "split" & recallOrderinMixed == "random" ~ "separate_unpredictable",
      TRUE ~ NA_character_  # Default/fallback, if none of the above match
    )
  )

```

## 3.2 Extrapolate the target and actually selected color values from the lists they are stored within. Calculate the error deviation in degrees.

``` {r}
# 1) Helpers to handle HSL strings and circular distances

# A simple modulo function
mod <- function(n, m) {
  ((n %% m) + m) %% m
}

# Compute the *small arc* between two angles in [0..360], returning a value in [0..180]
circDistSmallDeg <- function(a, b) {
  # This is the absolute difference based on the "wrap-around" of a circle
  diff_signed <- mod(((b - a) + 180), 360) - 180  # in [-180, 180)
  abs(diff_signed)
}

# The *large arc* is simply 360 minus the small arc.
circDistLargeDeg <- function(a, b) {
  360 - circDistSmallDeg(a, b)
}

# Compute the *signed* difference between two angles in [0..360], returning a value in [-180, 180)
circDistSignedDeg <- function(a, b) {
  mod(((b - a) + 180), 360) - 180
}

# Pull out the hue from an HSL string like "hsl(142, 80%, 50%)"
parse_hue <- function(hsl_string) {
  as.numeric(sub("hsl\\(([^,]+).*", "\\1", hsl_string))
}

# 2) Main data‐wrangling steps
dataWithErrorDeg <- declutteredData %>%
  dplyr::rowwise() %>%
  dplyr::mutate(
    # Grab the fill_color hue from each 1×8 sub-data.frame
    hue_stimulus = parse_hue(stimulusToIdentify$fill_color),
    hue_selected = parse_hue(selectedStimuli$fill_color),

    # Compute the small arc distance (absolute error)
    ErrorDeg = circDistSmallDeg(hue_stimulus, hue_selected),

    # Compute the small arc distance (signed error)
    ErrorDegSigned = circDistSignedDeg(hue_stimulus, hue_selected),

    # Compute the large arc distance
    ErrorDegLargeArc = circDistLargeDeg(hue_stimulus, hue_selected)
  ) %>%
  dplyr::ungroup() %>%
  # Optionally remove those list columns if you don’t need them
  dplyr::select(-stimulusToIdentify, -selectedStimuli)

```

# 4 ABSOLUTE ERRORS
## 4.1 Get an idea of error sizes for each participant

``` {r}

# 1) Summarize data by participant
Error_summary <- dataWithErrorDeg %>%
  dplyr::group_by(participant) %>%
  dplyr::summarize(
    meanError = mean(ErrorDeg, na.rm = TRUE),
    sdError   = sd(ErrorDeg, na.rm = TRUE),
    medianRT  = median(rt, na.rm = TRUE),
    n         = dplyr::n()
  ) %>%
  dplyr::ungroup()

Error_summary_grouped <- dataWithErrorDeg %>%
  dplyr::group_by(participant, trialType, numCircles) %>%
  dplyr::summarize(
    meanError = mean(ErrorDeg, na.rm = TRUE),
    sdError   = sd(ErrorDeg, na.rm = TRUE),
    medianRT  = median(rt, na.rm = TRUE),
    n         = n()
  ) %>%
  ungroup()


# 2) Identify participants whose mean ErrorDeg is greater than 85
bad_participants <- Error_summary %>%
  dplyr::filter(meanError > 85) %>%
  dplyr::pull(participant)

# 3) Filter your original dataset to exclude those participants
dataWithErrorDeg <- dataWithErrorDeg %>%
  dplyr::filter(!participant %in% bad_participants)

```

## 4.2 Analysis

### 4.2.1 Apply Contrast Coding to the Variables

``` {r}
# We adopt a contrast coding approach (using contr.equalprior) that aligns with Bayesian
# principles by encoding factor variables so that their numeric representations are centered 
# around zero. This reflects our prior belief of no inherent difference between levels—i.e., 
# an equal prior assumption. The function converts the variable into a factor and attaches a 
# contrast matrix that specifies unbiased numeric coding. This setup is particularly beneficial 
# when computing Bayes factors using the Savage–Dickey density ratio.

# First, recode variables as factors with meaningful labels

# This ensures that they are treated as categorical in analyses and that the levels 
# are clearly identifiable.

contrastCodedData <- dataWithErrorDeg %>%
  mutate(
    presentationType   = factor(presentationType, levels = c("grouped", "separate_predictable", "separate_unpredictable"), labels = c("Grouped", "Separate Predictable", "Separate Unpredictable")),
    recallPosition     = factor(recallPosition, levels = c(1,2), labels = c("Tested First", "Tested Second")),
    setSize            = factor(setSize, levels = c(3,6), labels = c("3", "6")),
    presentationOrder  = factor(AorBatRetrieval, levels = c("none", "A", "B"), labels = c("none", "A", "B"))
  )

# Then, attach bayestestR equal prior contrasts to the factors

# This creates a numeric coding for the factor levels that is centered around zero,
# reflecting an a priori belief that there is no inherent difference between levels 
# (i.e., equal prior assumptions).

contrasts(contrastCodedData$presentationType)     <- bayestestR::contr.equalprior(n = 3)
contrasts(contrastCodedData$recallPosition) <- bayestestR::contr.equalprior(n = 2)
contrasts(contrastCodedData$setSize)       <- bayestestR::contr.equalprior(n = 2)
contrasts(contrastCodedData$presentationOrder)   <- bayestestR::contr.equalprior(n = 3)

# Finally, standardize the error degrees

# When using a Cauchy distribution in Bayesian analysis, standardizing the data 
# ensures that the heavy-tailed nature of the Cauchy is appropriately centered 
# around zero. This can help the model better capture deviations and handle potential 
# outliers without being overly influenced by the raw scale of the original measurements.

contrastCodedData <- contrastCodedData %>%
  mutate(zerror = as.numeric(scale(ErrorDeg)))
```

### 4.2.2 Data visualization


``` {r}

# This type of data visualization is a bit tricky because we have a partial between-subjects factor: "presentationType".
# The "grouped" level is within‐subjects (everyone saw it), but the two "separate" levels are split between participants.
# To work around this, we split the data by presentationType (grouped vs. separate) and apply a within‐subject correction
# only to the conditions each subset actually contains. Then we recombine for plotting.
#
# However, keep in mind that the "grouped" condition uses data from all participants, whereas the two "separate"
# conditions come from distinct subgroups. As a result, the error bars in the final plot reflect different subsets
# of participants and separate within‐subject corrections. Direct comparisons between "grouped" and "separate"
# should therefore be interpreted with caution.


plot_memory_data_with_order <- function(
  data,
  subject_var        = "participant",
  dv_var             = "ErrorDeg",
  ws_vars_grouped    = c("recallPosition", "setSize"),
  ws_vars_separate   = c("recallPosition", "presentationOrder"), 
  bs_vars_separate   = c("presentationType"), 
  output_plots       = TRUE
) {
  
  # 1) "grouped" data only
  data_grouped <- data %>%
    filter(presentationType == "Grouped")
  
  # Summarize for "grouped"
  grouped_summary <- summarySEwithin(
    data        = data_grouped,
    measurevar  = dv_var,
    idvar       = subject_var,
    withinvars  = ws_vars_grouped, 
    betweenvars = NULL,
    na.rm       = TRUE
  ) %>%
    mutate(
      presentationType  = "Grouped",  # unify columns
      presentationOrder = "none"      # "Grouped" has no A/B
    )
  
  # 2) "separate" data (predictable + unpredictable)
  data_separate <- data %>%
    filter(presentationType %in% c("Separate Predictable", "Separate Unpredictable"))
  
  # Summarize for "separate"
  separate_summary <- summarySEwithin(
    data        = data_separate,
    measurevar  = dv_var,
    idvar       = subject_var,
    withinvars  = ws_vars_separate,   
    betweenvars = bs_vars_separate,   
    na.rm       = TRUE
  ) %>%
    mutate(setSize = "6")  # separate data presumably always 6
  
  # Combine them
  combined_summary <- dplyr::bind_rows(grouped_summary, separate_summary) %>%
    mutate(
      setSize            = factor(setSize, levels = c("3","6")),
      presentationType   = factor(
        presentationType,
        levels = c("Grouped", "Separate Predictable", "Separate Unpredictable")
      ),
      presentationOrder  = factor(
        presentationOrder,
        levels = c("none","A","B")
      )
    )
  
  plot_overlayed <- ggplot(
    combined_summary,
aes(
  x        = recallPosition,
  y        = ErrorDeg,
  color    = presentationType,
  linetype = presentationOrder,
  group    = interaction(presentationType, presentationOrder)
)
  ) +
    geom_point(
      aes(shape = presentationOrder),
      position = position_dodge(width = 0.3),
      size = 3
    ) +
    geom_line(
      position = position_dodge(width = 0.3)
    ) +
    geom_errorbar(
      aes(
        ymin = !!sym(dv_var) - se,
        ymax = !!sym(dv_var) + se
      ),
      width = 0.2,
      position = position_dodge(width = 0.3)
    ) +
    facet_wrap(~ setSize
    ) +
    labs(
      title    = "Absolute Deviation in Error Degrees by Presentation Type, Presentation Order, and Recall Position for Set Sizes 3 and 6",
      x        = "Recall Position",
      y        = "Error degrees (Cousineau–Morey CI)",
      color    = "Presentation Type",
      linetype = "Presentation Order",
      shape    = "Presentation Order"
    ) +
    theme_minimal(base_size = 14) +
    theme(
      # Center the title and add extra space below it
      plot.title = element_text(
        hjust  = 0.5,
        margin = margin(b = 20)
      )
    )
  
  if (output_plots) print(plot_overlayed)
  
  # Return list
  invisible(list(
    combined_summary = combined_summary,
    plot_overlayed   = plot_overlayed
  ))
}



result_order <- plot_memory_data_with_order(
  data               = contrastCodedData,
  subject_var        = "participant",
  dv_var             = "ErrorDeg",
  ws_vars_grouped    = c("recallPosition","setSize"),
  # If participants in the "separate" subset truly see both A and B within-subject:
  ws_vars_separate   = c("recallPosition", "presentationOrder"),
  bs_vars_separate   = c("presentationType"),
  output_plots       = TRUE
)

```

### 4.2.3 BRMS settings

``` {r}
nChains <- 4      # Number of Markov chains
nCores  <- 4      # Number of cores each model can use
nIter   <- 10000  # Total MCMC iterations per chain
nWarmup <- 2000   # Warmup (burn-in) iterations

# Ensures Stan will save compiled models to disk for reuse
rstan_options(auto_write = TRUE)
```

### 4.2.4 Specify Priors

``` {r}
# Do do a prior sensitivity analysis, we run the entire analysis with 3 different 
# priors. This lets us check whether the Priors we define can influence our conclusions

# Default priors, based on the experiment of Oberauer and Awh we are replicating
scaleVal_default <- 0.5
priorExpr_default <- paste0("cauchy(0, ", scaleVal_default, ")")
fixefPrior_default <- c( set_prior(priorExpr_default, class = "b") )   # fixed effects
ranefPrior_default <- set_prior("gamma(1,0.05)", class = "sd")          # random effects

# Alternative 1: Less informative fixed-effects prior (wider scale)
scaleVal_alt1 <- 1.0
priorExpr_alt1 <- paste0("cauchy(0, ", scaleVal_alt1, ")")
fixefPrior_alt1 <- c( set_prior(priorExpr_alt1, class = "b") )
ranefPrior_alt1 <- set_prior("gamma(1,0.05)", class = "sd")  # keeping the same for simplicity

# Alternative 2: More informative priors (narrower fixed effects)
scaleVal_alt2 <- 0.25
priorExpr_alt2 <- paste0("cauchy(0, ", scaleVal_alt2, ")")
fixefPrior_alt2 <- c( set_prior(priorExpr_alt2, class = "b") )
ranefPrior_alt2 <- set_prior("gamma(1,0.05)", class = "sd")  # keeping the same for simplicity

# Combine all prior sets into a list for sensitivity analysis
prior_list <- list(
  default = c(fixefPrior_default, ranefPrior_default),
  alt1    = c(fixefPrior_alt1, ranefPrior_alt1),
  alt2    = c(fixefPrior_alt2, ranefPrior_alt2)
)
```

## 4.3 Model calculation

``` {r}
models <- list()
prior_models <- list()

# First loop: Fit and save the models
for(prior_label in names(prior_list)) {
  models[[prior_label]] <- smart_runFun(
    fun = brm,
    args = list(
      formula = zerror ~ setSize * presentationType * recallPosition * presentationOrder +
        (1 + setSize * presentationType * recallPosition * presentationOrder || participant),
      data = dataWithErrorDeg,
      family = gaussian(),
      prior = prior_list[[prior_label]],
      chains = nChains,
      iter = nIter,
      warmup = nWarmup,
      cores = nCores,
      control = list(adapt_delta = 0.95, max_treedepth = 15),
      save_pars = save_pars(all = TRUE),
      file = glue::glue("./models/M.Full_{prior_label}")
    ),
    name = glue::glue("M.Full_{prior_label}")
    export = TRUE
  )
}

# Optionally, read the saved models if needed
for(prior_label in names(prior_list)) {
  models[[prior_label]] <- readRDS(glue::glue("./models/M.Full_{prior_label}.rds"))
}

# Second loop: Run unupdate on the fitted models to sample from the prior
for(prior_label in names(prior_list)) {
  prior_models[[glue::glue("{prior_label}_Priors")]] <- smart_runFun(
    fun = unupdate,
    args = list(model = models[[prior_label]]),
    name = glue::glue("M.Full_{prior_label}_Priors"),
    export = glue::glue("M.Full_{prior_label}_Priors")
  )
  # Save each unupdated model as an RDS in the same folder
  saveRDS(
    prior_models[[glue::glue("{prior_label}_Priors")]],
    file = glue::glue("./models/M.Full_{prior_label}_Priors.rds")
  )
}

for(prior_label in names(prior_list)) {
  prior_models[[glue::glue("{prior_label}_Priors")]] <- readRDS(
    glue::glue("./models/M.Full_{prior_label}_Priors.rds")
  )
}

```

## 4.4 Pairwise contrasts

``` {r}
# Define all "specs" in a vector
all_specs <- c(
  "~presentationType|setSize+recallPosition+presentationOrder",
  "~setSize|presentationType+recallPosition+presentationOrder",
  "~recallPosition|presentationType+setSize+presentationOrder",
  "~presentationOrder|presentationType+setSize+recallPosition"
)

# Create a container list to hold all results
pairwise_results <- list()

for (prior_label in names(prior_list)) {
  
  message("Submitting pairwise comparisons for: ", prior_label)
  
  # Initialize a sub-list in pairwise_results for each prior_label
  pairwise_results[[prior_label]] <- list()
  
  for (spec in all_specs) {
    
    # Create a unique job name for each submission
    job_name <- paste0("pairwise_", prior_label, "_", gsub("[~|+]", "_", spec))
    
    # Submit the job using smart_runFun
    result <- smart_runFun(
      fun  = pairwise_comparisons,
      args = list(
        model       = models[[prior_label]],
        prior_model = prior_models[[paste0(prior_label, "_Priors")]],
        specs       = spec,
        interaction = FALSE
      ),
      name   = job_name,
      export = TRUE
    )
    
    # Store the result for later (so you keep all specs results together)
    pairwise_results[[prior_label]][[spec]] <- result
  }
}

```

``` {r}
all_specs_main <- c(
  "~presentationType",
  "~setSize",
  "~recallPosition",
  "~presentationOrder"
)

pairwise_results_main <- list()

for (prior_label in names(prior_list)) {
  
  message("Submitting *main effect* pairwise comparisons for: ", prior_label)
  
  # Create a sub-list for each prior
  pairwise_results_main[[prior_label]] <- list()
  
  # Loop over the main-effect specs
  for (spec in all_specs_main) {
    
    # Create a unique job name
    job_name <- paste0("pairwise_main_", prior_label, "_", gsub("[~+]", "_", spec))
    
    # Submit the job using smart_runFun
    result <- smart_runFun(
      fun  = pairwise_comparisons,
      args = list(
        model       = models[[prior_label]],
        prior_model = prior_models[[paste0(prior_label, "_Priors")]],
        specs       = spec,            # <-- Using single-factor specs
        interaction = FALSE
      ),
      name   = job_name,
      export = TRUE
    )
    
    # Store the result
    pairwise_results_main[[prior_label]][[spec]] <- result
  }
}

```



# 5 SIGNED ERRORS

## 5.2 Basic visualization:

``` {r}
dfForPlot <- dataWithErrorDeg %>%
  mutate(
    # Ensure the factors have consistent labels
    presentationType = factor(
      presentationType,
      levels = c("grouped", "separate_predictable", "separate_unpredictable"),
      labels = c("Grouped", "Separate Predictable", "Separate Unpredictable")
    ),
    recallPosition = factor(
      recallPosition,
      levels = c(1, 2),
      labels = c("Tested First", "Tested Second")
    ),
    setSize = factor(
      setSize,
      levels = c(3, 6),
      labels = c("3", "6")
    )
  )

ggplot(
  dfForPlot,
  aes(x = ErrorDegSigned)
) +
  geom_histogram(
    binwidth = 15,      # choose a bin width that makes sense for your data
    color    = "black",
    fill     = "steelblue",
    alpha    = 0.7
  ) +
  facet_grid(
    rows    = vars(presentationType, setSize), 
    cols    = vars(recallPosition)
  ) +
  theme_minimal(base_size = 14) +
  labs(
    title = "Distribution of Signed Errors by Condition (Histogram)",
    x     = "Signed Error (Degrees)",
    y     = "Count"
  )

ggplot(
  dfForPlot,
  aes(x = ErrorDegSigned)
) +
  geom_density(
    color = "steelblue",
    fill  = "steelblue",
    alpha = 0.3
  ) +
  facet_grid(
    rows = vars(presentationType, setSize),
    cols = vars(recallPosition)
  ) +
  theme_minimal(base_size = 14) +
  labs(
    title = "Distribution of Signed Errors by Condition (Density)",
    x     = "Signed Error (Degrees)",
    y     = "Density"
  )

```

## 5.3 Elaborate visualization

``` {r}
# Assume you already have a data frame `contrastCodedData` 
# with a column `ErrorDegSigned` (the signed errors in degrees).
# We'll again transform to a circular object, then fit the distribution.

# 1a) Convert to a circular object (still in degrees)
dataWithErrorDegCircular <- contrastCodedData %>%
  dplyr::mutate(
    error_circ = circular(
      x         = ErrorDegSigned,        # your signed error in degrees
      units     = "degrees",
      type      = "angles",
      template  = "geographics",
      modulo    = "2pi"                  # effectively uses 360 wrapping for degrees
    )
  )

# 1b) For each participant x condition, fit a wrapped Cauchy
#     and store the results.

dataCauchy <- dataWithErrorDegCircular %>%
  dplyr::group_by(
    participant,
    presentationType,
    recallPosition,
    setSize,
    presentationOrder
  ) %>%
  dplyr::summarize(
    # Fit the wrapped Cauchy distribution to `error_circ`.
    # If you'd like, you can provide initial guesses for mu and rho. 
    fit = list(mle.wrappedcauchy(error_circ)),

    # Also keep track of the # of trials per cell
    n   = n(),
    .groups = "drop"  # or ungroup() afterwards
  ) %>%
  # Extract the parameters: mu (mean direction) and rho (concentration)
  dplyr::mutate(
    mu  = map_dbl(fit, ~ as.numeric(.x$mu)),   # in degrees
    rho = map_dbl(fit, ~ .x$rho)              # in [0..1)
  )

# Now `dataCauchy` has columns:
#  - participant, presentationType, recallPosition, setSize, presentationOrder
#  - fit (list-col), n, mu, rho
#
#  rho is analogous to a “concentration” measure: 
#    * 0.0 means uniform 
#    * close to 1.0 means highly concentrated
plot_rho_data_with_order <- function(
  data, 
  subject_var        = "participant",
  dv_var             = "rho",                    # Now "rho" is our measure
  # For "grouped" data
  ws_vars_grouped    = c("recallPosition", "setSize"),
  # For "separate" data
  ws_vars_separate   = c("recallPosition", "presentationOrder"),
  bs_vars_separate   = c("presentationType"),
  output_plots       = TRUE
) {
  
  # 1) Filter data for the "grouped" condition
  data_grouped <- data %>%
    dplyr::filter(presentationType == "Grouped")
  
  # Summarize for "grouped":
  grouped_summary <- summarySEwithin(
    data        = data_grouped,
    measurevar  = dv_var,                
    idvar       = subject_var,           
    withinvars  = ws_vars_grouped,       
    na.rm       = TRUE
  ) %>%
    dplyr::mutate(
      presentationType  = "Grouped",  
      presentationOrder = "none"
    )
  
  # 2) Filter data for the “separate” conditions
  data_separate <- data %>%
    dplyr::filter(presentationType %in% c("Separate Predictable", "Separate Unpredictable"))
  
  # Summarize for "separate":
  separate_summary <- summarySEwithin(
    data        = data_separate,
    measurevar  = dv_var,
    idvar       = subject_var,
    withinvars  = ws_vars_separate,       
    betweenvars = bs_vars_separate,       
    na.rm       = TRUE
  ) %>%
    dplyr::mutate(setSize = "6")  # in separate conditions, setSize is typically 6
  
  # 3) Combine
  combined_summary <- dplyr::bind_rows(grouped_summary, separate_summary) %>%
    dplyr::mutate(
      setSize = factor(setSize, levels = c("3","6")),
      presentationType = factor(
        presentationType,
        levels = c("Grouped", "Separate Predictable", "Separate Unpredictable")
      ),
      presentationOrder = factor(
        presentationOrder,
        levels = c("none","A","B")
      )
    )
  
  # 4) Plot
  dv_sym <- rlang::sym(dv_var)
  
  plot_overlayed <- ggplot(
    combined_summary,
    aes(
      x        = recallPosition,
      y        = !!dv_sym,  
      color    = presentationType,
      linetype = presentationOrder,
      group    = interaction(presentationType, presentationOrder)
    )
  ) +
    geom_point(
      aes(shape = presentationOrder),
      position = position_dodge(width = 0.3),
      size     = 3
    ) +
    geom_line(position = position_dodge(width = 0.3)) +
    geom_errorbar(
      aes(
        ymin = !!dv_sym - se,
        ymax = !!dv_sym + se
      ),
      width    = 0.2,
      position = position_dodge(width = 0.3)
    ) +
    facet_wrap(~ setSize) +
    labs(
      title    = "Wrapped Cauchy Concentration (rho) by Condition",
      x        = "Recall Position",
      y        = expression(rho),
      color    = "Presentation Type",
      shape    = "Presentation Order",
      linetype = "Presentation Order"
    ) +
    theme_minimal(base_size = 14) +
    theme(
      plot.title = element_text(
        hjust  = 0.5,
        margin = margin(b = 20)
      )
    )
  
  if (output_plots) print(plot_overlayed)
  
  invisible(list(
    combined_summary = combined_summary,
    plot_overlayed   = plot_overlayed
  ))
}
# After you have your dataCauchy with columns:
#    participant, presentationType, recallPosition, setSize, presentationOrder, rho

result_rho <- plot_rho_data_with_order(
  data               = dataCauchy,
  subject_var        = "participant",
  dv_var             = "rho",
  ws_vars_grouped    = c("recallPosition","setSize"),
  ws_vars_separate   = c("recallPosition","presentationOrder"),
  bs_vars_separate   = c("presentationType"),
  output_plots       = TRUE
)

```


## 5.4 BMM
### 5.4.1 Restructure data for BMM

``` {r}

## ------------------------------------------------------------------ ##
##  1.  Start from your existing 'contrastCodedData'  (or earlier)    ##
## ------------------------------------------------------------------ ##

collapsedData <- contrastCodedData %>%           # or dataWithErrorDeg, etc.
  mutate(
    ## ---- 1.1  new 6‑level factor -----------------------------------------
    condition = case_when(
      presentationType == "Grouped" &
        setSize          == "3"                     ~ "grouped_setSize3",

      presentationType == "Grouped" &
        setSize          == "6"                     ~ "grouped_setSize6",

      presentationType == "Separate Unpredictable" &
        presentationOrder == "A"                    ~ "split_unpredictable_A",

      presentationType == "Separate Unpredictable" &
        presentationOrder == "B"                    ~ "split_unpredictable_B",

      presentationType == "Separate Predictable" &
        presentationOrder == "A"                    ~ "split_predictable_A",

      presentationType == "Separate Predictable" &
        presentationOrder == "B"                    ~ "split_predictable_B",

      TRUE                                           ~ NA_character_   # any row that
                                                                      # should be dropped
    ),

    ## ---- 1.2  tidy the two remaining predictors -------------------------
    condition      = factor(
                       condition,
                       levels = c("grouped_setSize3",  "grouped_setSize6",
                                  "split_unpredictable_A", "split_unpredictable_B",
                                  "split_predictable_A",  "split_predictable_B")
                     ),
    recallPosition = factor(
                       recallPosition,
                       levels = c("Tested First", "Tested Second")
                     ),

    ## ---- 1.3  response in *radians* (needed by bmm) ----------------------
    response_error = ErrorDegSigned * pi / 180      # keep signed!

  ) %>%
  ## Drop any row that did not match a real condition -----------------------
  drop_na(condition)


collapsedData <- collapsedData %>% 
  ## make absolutely sure 'condition' is a factor *after* drop_na()
  mutate(
    condition = factor(
      condition,
      levels = c("grouped_setSize3",  "grouped_setSize6",
                 "split_unpredictable_A", "split_unpredictable_B",
                 "split_predictable_A",  "split_predictable_B")
    )
  )

## ------------------------------------------------------------------ ##
##  2.  Attach equal‑prior contrasts (centred, sum‑to‑zero)           ##
## ------------------------------------------------------------------ ##
contrasts(collapsedData$condition)      <- contr.equalprior(n = 6)
contrasts(collapsedData$recallPosition) <- contr.equalprior(n = 2)

## ------------------------------------------------------------------ ##
##  3.  Ready for modelling                                           ##
## ------------------------------------------------------------------ ##
head(collapsedData %>% 
       select(participant, condition, recallPosition, response_error) )

trial_counts <- collapsedData %>% 
  dplyr::count(participant, condition, recallPosition, name = "n_trials")
```

### 5.4.2 Run analysis

``` {r}

###############################################################################
# 0) packages -----------------------------------------------------------------
###############################################################################
pacman::p_load(bmm, brms, tidyverse, here, tidybayes, patchwork, gghalves)

options(mc.cores = parallel::detectCores())

warmup  <- 3000          # ★ tweak if you like
post    <- 10000          # ★
chains  <- 7
if (chains > parallel::detectCores()) chains <- parallel::detectCores()

mod_onefactor <- mixture2p(resp_error = "response_error")

form_onefactor <- bmf(
  kappa  ~ 0 + condition * recallPosition +
            (0 + condition * recallPosition || participant),
  thetat ~ 0 + condition * recallPosition +
            (0 + condition * recallPosition || participant)
)

fit_onefactor <- bmm(
  formula      = form_onefactor,
  data         = collapsedData,
  model        = mod_onefactor,
  sample_prior = TRUE,
  save_pars    = save_pars(all = TRUE),
  warmup       = warmup,
  iter         = warmup + post,
  chains       = chains,
  cores        = parallel::detectCores(),
  control      = list(adapt_delta   = .99,
                      max_treedepth = 12),
  backend      = "cmdstanr",
  refresh      = 500,
  file         = here::here("output", "fit_onefactor_bmm")
)

```

### 5.4.3 Convergence diagnostics

``` {r}
## ------------------------------------------------------------------ ##
##  0.  Load the fitted model (if this is a fresh session)            ##
## ------------------------------------------------------------------ ##
library(brms)      ; library(bmm)
library(tidyverse) ; library(tidybayes)
library(bayesplot) ; library(posterior)
library(here)      ; library(gghalves)
theme_set(theme_minimal(base_size = 13))

fit_onefactor <- read_rds(here("output", "fit_onefactor_bmm.rds"))
#   ^^^ change if you saved it under a different filename / extension

## 1.1  Scalar summaries ------------------------------------------------------
max_rhat   <- max(rhat(fit_onefactor),         na.rm = TRUE)
min_neff   <- min(neff_ratio(fit_onefactor),   na.rm = TRUE)
divergences <- sum(fit_onefactor$fit_diagnostics$divergent__)
treedepths  <- sum(fit_onefactor$fit_diagnostics$treedepth__ >
                   fit_onefactor$fit_diagnostics$max_treedepth__)

cat(glue::glue("
   ── Convergence ─────────────────────────────────────────
   • max R‑hat        : {round(max_rhat, 3)}
   • min n_eff / N    : {round(min_neff, 3)}
   • divergent draws  : {divergences}
   • saturated trees  : {treedepths}
"))

## 1.2  Visual checks  --------------------------------------------------------
bayesplot::mcmc_rhat(rhat(fit_onefactor))              # should all be ≤ 1.01
bayesplot::mcmc_neff(neff_ratio(fit_onefactor))        # most ≥ 0.1
bayesplot::mcmc_trace(
  as_draws_array(fit_onefactor, variable = "^b_"),     # all fixed effects
  facet_args = list(ncol = 3, strip.position = "left")
)

# Look for gross mis‑fit in the tails or multimodalities that the mixture cannot capture.
pp_check(
  fit_onefactor,
  group = "condition:recallPosition",
  type  = "dens_overlay_grouped"
)

# Extract, back‑transform and tidy the fixed‑effect draws
draws_tidy <- fit_onefactor %>%
  tidy_draws() %>%
  select(starts_with("b_"), .draw) %>%
  pivot_longer(
    cols      = starts_with("b_"),
    names_to  = "term",
    values_to = "beta"
  ) %>%
  separate(
    term,            # "b_kappa_conditiongrouped_setSize6:recallPosition…"
    into  = c(".drop","par","cell"), sep = "_", extra = "merge",
    remove = TRUE
  ) %>%
  mutate(
    par   = recode(par,
                   kappa  = "SD° (memory imp.)",
                   thetat = "P(mem)"),
    value = if_else(par == "SD° (memory imp.)",
                    (sqrt(1/exp(beta)) / pi) * 180,    # κ → SD in degrees
                    plogis(beta))                      # θ → probability
  )

# Quick forest plot

draws_tidy %>%
  mutate(cell = str_replace_all(cell, "condition", "")) %>%  # cosmetic
  group_by(par, cell) %>%
  mean_qi(value, .width = 0.95) %>%
  ggplot(aes(x = value, y = reorder(cell, value))) +
  geom_point() +
  geom_errorbarh(aes(xmin = .lower, xmax = .upper), height = .1) +
  facet_wrap(~ par, scales = "free_x") +
  labs(y = NULL, x = "Posterior mean ± 95 % CrI")

```
### 5.4.4 Specify and test a priori contrasts

```{r}
# Build a helper table of the 12 cell names
cell_names <- draws_tidy %>%
  distinct(cell) %>% arrange(cell) %>% pull()
cell_names              # print once to check spelling

# Hypotheses of interest:
## 4.2.1  Predictable vs Unpredictable  (averaged over A/B & recall positions)
##        – κ and pMem tested separately
hyp_predictable <- c(
  # κ (memory precision)
  "kappa_conditionsplit_predictable_A:recallPositionTestedFirst
   = kappa_conditionsplit_unpredictable_A:recallPositionTestedFirst",

  "kappa_conditionsplit_predictable_A:recallPositionTestedSecond
   = kappa_conditionsplit_unpredictable_A:recallPositionTestedSecond",

  "kappa_conditionsplit_predictable_B:recallPositionTestedFirst
   = kappa_conditionsplit_unpredictable_B:recallPositionTestedFirst",

  "kappa_conditionsplit_predictable_B:recallPositionTestedSecond
   = kappa_conditionsplit_unpredictable_B:recallPositionTestedSecond",

  # θ → pMem
  "thetat_conditionsplit_predictable_A:recallPositionTestedFirst
   = thetat_conditionsplit_unpredictable_A:recallPositionTestedFirst",

  "...and so on for the remaining three cells..."
)

## 4.2.2  “Split” vs “Grouped 6” (benefit) -------------------------------
## Null: no difference  →  negative estimate means *benefit*
benefit_pairs <- expand_grid(
  split = c("split_predictable_A",  "split_predictable_B",
            "split_unpredictable_A","split_unpredictable_B"),
  pos   = c("TestedFirst", "TestedSecond")
) %>%
  mutate(
    hyp_kappa  = glue::glue(
      "kappa_condition{split}:recallPosition{pos} =
       kappa_conditiongrouped_setSize6:recallPosition{pos}"
    ),
    hyp_theta  = glue::glue(
      "thetat_condition{split}:recallPosition{pos} =
       thetat_conditiongrouped_setSize6:recallPosition{pos}"
    )
  ) %>%
  pivot_longer(c(hyp_kappa, hyp_theta), values_to = "hyp") %>%
  pull(hyp)

## 4.2.3  Combine all into one vector -----------------------------------
all_hypotheses <- c(hyp_predictable, benefit_pairs)

# Run hypothesis tests
hyp_res <- hypothesis(fit_onefactor, all_hypotheses)
print(hyp_res, digits = 3)
plot(hyp_res)         # forest plot of posterior contrasts


```
### 5.4.5 Plot contrasts
```{r}
diff_draws <- draws_tidy %>%
  unite(cell_full, cell, par, remove = FALSE) %>%      # unique key
  select(.draw, cell_full, par, value) %>%
  pivot_wider(names_from = cell_full, values_from = value)

## Example: Split Predictable A – Split Unpredictable A  (Tested First)
diff_draws <- diff_draws %>%
  mutate(
    d_SD  = `conditionSplit_predictable_A:recallPositionTestedFirst_SD° (memory imp.)` -
            `conditionSplit_unpredictable_A:recallPositionTestedFirst_SD° (memory imp.)`,
    d_pMem = `conditionSplit_predictable_A:recallPositionTestedFirst_P(mem)` -
             `conditionSplit_unpredictable_A:recallPositionTestedFirst_P(mem)`
  )

ggplot(diff_draws, aes(x = d_SD)) +
  geom_histogram(bins = 80) +
  geom_vline(xintercept = 0, linetype = 2) +
  labs(title = "Predictable A – Unpredictable A (Tested First)",
       x = "Δ SD (deg)", y = "Posterior draws")
```